Reproducible development environments with rix

### 2025-02-19 paper.qmd
Update paper.qmd

## The [Nix]{.pkg} package manager {#sec-nix}

@@

With Nix, it is essentially possible to replace [renv]{.pkg} and
[Docker]{.proglang} combined, or in the case of [Python]{.proglang}, replace
`requirements.txt` files which list package dependencies for [Python]{.proglang}
projects and virtual environments. It is also possible to build multi-language
environments, containing [R]{.proglang}and Python, a LaTeX distribution, and even install
one's favorite text editor to edit the project's source code. Essentially, one
can define a complete, project-specific, and reproducible environment and use it
interactively, or non-interactively. It will always be possible to rebuild this
environment in the future (as long as the `nixpkgs` GitHub repository is online)
to run an analysis sometime in the future.

@@

## Reproducible development environments with [Nix]{.pkg} {#sec-repro-nix}

@@

```
nix-shell -p [R]{.proglang}rPackages.rix"
```

>>>>

## The Nix package manager {#sec-nix}

@@

With Nix, it is essentially possible to replace [renv]{.pkg} and
[Docker]{.proglang} combined, or in the case of [Python]{.proglang}, replace
`requirements.txt` files which list package dependencies for [Python]{.proglang}
projects and virtual environments. It is also possible to build multi-language
environments, containing [R]{.proglang} and Python, a LaTeX distribution, and even install
one's favorite text editor to edit the project's source code. Essentially, one
can define a complete, project-specific, and reproducible environment and use it
interactively, or non-interactively. It will always be possible to rebuild this
environment in the future (as long as the `nixpkgs` GitHub repository is online)
to run an analysis sometime in the future.

@@

## Reproducible development environments with Nix{#sec-repro-nix}

@@

```
nix-shell -p R rPackages.rix
```
